### 2022-04-15 paper1.tex
Most post-defense edits

With the expansion of big data, some computational social science research has
developed extremely innovative methods that have led to groundbreaking results
using reliable sources of big data. As an
example,\citet{blumenstockPredictingPovertyWealth2015} use county-level
cell-phone records to construct the distribution of poverty and wealth in
Rwanda, a country where national surveys and censuses are rare and costly.
However, \citet{blumenstockPredictingPovertyWealth2015} go to great lengths to
demonstrate that their use of the cell phone data creates a reliable and valid
construct; few social science papers utilizing big data dig into the construct
validity of their metrics to this extent and even fewer publications focus on
methodological guidelines of how to use sources of big data \citep[For
exceptions, see ][]{asseoTrackingCOVID19Using2020,
stilesAssessingCriterionValidity2018}. However, research has shown the small
adjustments to an algorithm or metric may void any research insight we can pull
from such data \citep{lazerParableGoogleFlu2014}.

@@

Building on prior research outlining the various issues with different sources
of big data \citep{boydCriticalQuestionsBig2012,lazerIssuesConstructValidity2015}, this
paper evaluates the construct validity of Google Search Trends as an indicator
of three different cases, namely attitudes, disease prevalence and political
preferences. These three cases will be tested using attitudinal indicators from
the CDC \citeyearpar{vaches_data} and New York Times \citeyearpar{mask_data}, 
health indicators from the CDC
\citeyearpar{suic_data}, US cases rates of COVID-19 from The New York Times
\citeyearpar{covid_data}, and political indicators from the historical US
Presidential Election results \citeyearpar{pres_data}. 
% , and the American National Election Survey \citeyearpar{anes_data}.
This paper will contribute
guidance for creating standards of how to use Google Trends for social research,
and identify potential pitfalls that can compromise the analysis including the
focus of this paper, which shows that Google Trends has a lack of ecological
validity.

@@

\subsubsection{Google Trends}
This paper focuses on a triangulation of Google search trends
\citep{googletrends} with other sources of credible data. Google trends portray
the search frequency for specific search terms across designated media markets
areas (DMAs), a nonoverlapping aggregation of U.S. counties to 210 media markets
based on Nielsen's classification of ``similar population clusters''
\citep{dma_key}. Raw data is on a scale from zero to one hundred, with one
hundred being the maximum search popularity out of all DMAs. When available, I
use Google search topics to measure trends as opposed to search terms. Search
topics are a more robust measurement than a single search term: topics are
aggregations of the rates of multiple, highly correlated search terms together
into a cohesive topic done by Google through it's Knowledge Graph product. For
example, while 'Beyoncé', 'Beyonce' and 'beyonce knowles' are all separate
search terms, 'Beyoncé Knowles' encompasses all of these into a single search
topic. Google Search Trends are only available cross-sectionally (a single
period across a geography) or as time-series (a single geo-location across
time). To remedy this and build a longitudinal dataset of each search topic to
match the longitudinal validated measures, I follow the method proposed in
\citet[][p. 5]{park_etal}\footnote{This method involves building a dataset of
unscaled cross-sectional values, selecting a DMA to use to establish the
rescaling ratio (I use 'Los Angeles CA'), and then finding the time-series
values for the one DMA. To find the rescaling ratio for each week in the
time-series, you divide the time-series value for each week by the
cross-sectional value for each week, resulting in a rescaling vector to be used
for all weeks in the dataset across geographies. To rescale each longitudinal
value, multiply the respective week's rescaling ratio by the cross-sectional
value. To validate this method, I compared the rescaled longitudinal data
against multiple samples of time-series data. For a more in-depth explanation of
this procedure, see \citet[p. 5]{park_etal}}. I interpolate missing data points
in the longitudinal datasets using The Zoo package for R \citep{zoo}.

>>>>

With the expansion of big data, some computational social science research has
developed extremely innovative methods that have led to groundbreaking results
using reliable sources of big data. As an
example,\citet{blumenstockPredictingPovertyWealth2015} use county-level
cell-phone records to construct the distribution of poverty and wealth in
Rwanda, a country where national surveys and censuses are rare and costly.
In this paper,  \citet{blumenstockPredictingPovertyWealth2015} put in an effort to 
investigate the criterion validity of their measure; that is, they investigate 
how well an \textit{operationalization} of a specific construct is able to 
predict a \textit{theoretical representation} of the construct — the criterion. 
Investigating the criterion validity in their paper demonstrate that their use
of the cell phone data creates a reliable and valid construct. 
Few other social science papers utilizing big data dig into the criterion
validity of their metrics to this extent;even fewer publications focus on
methodological guidelines of how to use sources of big data \citep[For
exceptions, see ][]{asseoTrackingCOVID19Using2020,
stilesAssessingCriterionValidity2018}. However, research has shown the small
adjustments to an algorithm or metric may void any research insight we can pull
from such data \citep{lazerParableGoogleFlu2014}.

@@

Building on prior research outlining the various issues with different sources
of big data \citep{boydCriticalQuestionsBig2012,lazerIssuesConstructValidity2015}, this
paper evaluates the criterion validity of Google Search Trends as an indicator
of three different cases, namely attitudes, disease prevalence and political
preferences. These three cases will be tested using attitudinal indicators from
the CDC \citeyearpar{vaches_data} and New York Times \citeyearpar{mask_data}, 
health indicators from the CDC
\citeyearpar{suic_data}, US cases rates of COVID-19 from The New York Times
\citeyearpar{covid_data}, and political indicators from the historical US
Presidential Election results \citeyearpar{pres_data}. 
% , and the American National Election Survey \citeyearpar{anes_data}.
This paper will contribute
guidance for creating standards of how to use Google Trends for social research,
and identify potential pitfalls that can compromise the analysis including the
focus of this paper, which shows that Google Trends has a lack of criterion validity
for multiple ways which researchers may want to use it.

@@

\subsubsection{Google Trends}
This paper focuses on a triangulation of Google search trends
\citep{googletrends} with other sources of credible data. Google trends portray
the search frequency for specific search terms across designated media markets
areas (DMAs), a nonoverlapping aggregation of U.S. counties to 210 media markets
based on Nielsen's classification of ``similar population clusters''
\citep{dma_key}. Raw data is on a scale from zero to one hundred, with one
hundred being the maximum search popularity out of all DMAs. When available, I
use Google search topics to measure trends as opposed to search terms. Search
topics are a more robust measurement than a single search term: topics are
aggregations of the rates of multiple, highly correlated search terms together
into a cohesive topic done by Google through it's Knowledge Graph product. For
example, while 'Beyoncé', 'Beyonce' and 'beyonce knowles' are all separate
search terms, 'Beyoncé Knowles' encompasses all of these into a single search
topic. Google Search Trends are only available cross-sectionally (a single
period across a geography) or as time-series (a single geo-location across
time). To remedy this and build a longitudinal dataset of each search topic to
match the longitudinal validated measures, I follow the method proposed in
\citet[][p. 5]{park_etal}\footnote{This method involves building a dataset of
unscaled cross-sectional values, selecting a DMA to use to establish the
rescaling ratio (I use 'Los Angeles CA'), and then finding the time-series
values for the one DMA. To find the rescaling ratio for each week in the
time-series, you divide the time-series value for each week by the
cross-sectional value for each week, resulting in a rescaling vector to be used
for all weeks in the dataset across geographies. To rescale each longitudinal
value, multiply the respective week's rescaling ratio by the cross-sectional
value. To validate this method, I compared the rescaled longitudinal data
against multiple samples of time-series data. For a more in-depth explanation of
this procedure, see \citet[p. 5]{park_etal}}. I interpolate missing data points
in the longitudinal datasets using The Zoo package for R \citep{zoo} which estimates
the values of missing data points based on the immediately preceding and succeeding
time points for each separate time-series group. This differs from multiple imputation, 
which would take other features into account when estimating the missing data point.

### 2022-04-15 paper2.tex
Most post-defense edits

@@

Adapting these facets of UGT and social support to my own case, I theorize that
online search allows for increased anonymity, a lowered social cost, and the
potential avoidance of embarrassment and other negative social interactions,
especially in the case on search engines.
\citet{rainsCopingIllnessDigitally2018} finds that patients tend to search for
technical information about an illness online but they then turn to their social
network for experiential information from others facing similar circumstances in
the case of cancer. The type of information sought is therefore important. If
specific expertise on a specific topic is desired by a searcher, they may reach
out to personal connections that they see as expert such as a doctor, or if an
individual distrusts the medical establishment, they may be more likely to
activate informational support among their social network or turn to online
groups that validate their worldview \citep{bogersHowSocialAre2014}. Finally,
UGT and Brasher's definition of social support
\citeyearpar{brashersInformationSeekingAvoiding2002} help us to theorize that
the psychosocial needs like identity management or relational maintenance of an
individual may influence the chosen information search modality: when the
informational need is related to forming and deepening social ties search is
likely to be done from network ties.

@@

The second model predicts whether a respondent sought information about COVID-19
vaccinations by asking a person like friend, neighbor, or family member that
they know. Only three coefficients in this model were significant and help us
draw any conclusions on who is most likely to activate their personal social
network for informational support. In this study, I find that receiving
information about the vaccine from a doctor, their personal network, or a social
networking site is associated with seeking out more information. Those who
received information from a doctor or other medical professional were 3.08 times
more likely to seek information from a person such as a friend (\emph{p}
\textless{} 0.001). Moreover, it seems that receiving information from your
personal social network, such as a friend or relative, is associated with
seeking information from those same people; in fact, I find that those who did
are 3.32 more likely to do so (\emph{p} \textless{} 0.001, see Table
\ref{tab:table-model-2}, ``Person'' model). Finally, the
respondents who received information about the vaccine on a social networking
site were 55\% more likely to seek information from their personal network than
those who had not (\emph{p} \textless{} 0.01). The unexpected result of this
model is that very few factors predict personal social network activation, and
this model has the lowest McFadden's R\^{2}, indicating possible omitted
variables.

>>>>

Adapting these facets of UGT and social support to my own case, I theorize that
online search allows for increased anonymity, a lowered social cost, and the
potential avoidance of embarrassment and other negative social interactions,
especially in the case on search engines.

@@

\citet{rainsCopingIllnessDigitally2018} finds that while patients tend to search for
technical information about an illness online, they then turn to their social
network for experiential information from others facing similar circumstances in
the case of cancer. The type of information sought is therefore important. If
specific expertise on a specific topic is desired by a searcher, they may reach
out to personal connections that they see as expert such as a doctor. Or, if an
individual distrusts the medical establishment, they may be more likely to
activate informational support among their social network or turn to online
groups that validate their worldview \citep{bogersHowSocialAre2014}. Finally,
UGT and Brasher's definition of social support
\citeyearpar{brashersInformationSeekingAvoiding2002} help us to theorize that
psychosocial needs like identity management or relational maintenance of each
individual may influence their chosen information search modality: when the
informational need is related to forming and deepening social ties search is
likely to be done from network ties.

@@

The second model predicts whether a respondent sought information about COVID-19
vaccinations by asking a person like friend, neighbor, or family member that
they know. Only three coefficients in this model were significant and help us
draw any conclusions on who is most likely to activate their personal social
network for informational support. In this study, I find that receiving
information about the vaccine from a doctor, their personal network, or a social
networking site is associated with seeking out more information. Those who
received information from a doctor or other medical professional were 3.08 times
more likely to seek information from a person such as a friend (\emph{p}
\textless{} 0.001). Moreover, it seems that receiving information from your
personal social network, such as a friend or relative, is associated with
seeking information from those same people; in fact, I find that those who did
are 3.32 more likely to do so (\emph{p} \textless{} 0.001, see Table
\ref{tab:table-model-2}, ``Person'' model). Finally, the
respondents who received information about the vaccine on a social networking
site were 55\% more likely to seek information from their personal network than
those who had not (\emph{p} \textless{} 0.01). The unexpected result of this
model is that very few factors predict personal social network activation, and
this model has the lowest McFadden's R\^{2}, indicating possible omitted
variables. Possible omissions may include personality type, psychosocial
resources, and personal network composition.
